\mytitle

### 2012-02-22 papers/SAS2012/implicitization.tex
un booléen pour activer/désactiver les commentaires
Encore un peu de retaillage

\newcommand{\avirer}[1]{ {\color{red} #1} }
\newcommand{\MM}[1]{{\color{blue} TODO(MM): #1}}
%\newcommand{\JH}[1]{{\color{teal} TODO(JH): #1}}
%\newcommand{\DM}[1]{{\color{violet} TODO(DM): #1}}
%\newcommand{\avirer}[1]{}
%\newcommand{\MM}[1]{}
%\newcommand{\JH}[1]{}
%\newcommand{\DM}[1]{}

@@

\begin{figure}
\centering
\begin{minipage}[c]{.21\textwidth}
\begin{tikzpicture}[->,>=stealth',auto,node distance=.2cm and .5cm,
                    semithick,font=\footnotesize]

@@

  \path [transition] 
		(n0) edge  [out=0, in=0]            node {} (n9);
  \path [transition] 
		(n0) edge  [out=180, in=180]        node {} (n9);
  \path [transition] 
		(n0) edge  [out=205, in=155]            node {} (n9);
  \path [transition] 
		(n0) edge  [out=230, in=130]            node {} (n9);
  \path [transition] 
		(n0) edge  [out=255, in=105]            node {} (n9);
  \path [transition] 
		(n0) edge  [out=-25, in=25]            node {} (n9);
  \path [transition] 
		(n0) edge  [out=-50, in=50]            node {} (n9);
  \path [transition] 
		(n0) edge  [out=-75, in=75]            node {} (n9);
\end{tikzpicture}
\end{minipage}
\caption{Expansion of the transition graph into a multigraph.}
\label{fig:multigraph}
\end{figure}

Classical interval analysis on this program yields $\lstinline|x_old| \in [-100000,100000]$.
We have transformed the first program into the second, manually pruning out infeasible paths; yet in general the resulting program could be exponentially larger than the first (as in Fig.~\ref{fig:multigraph}), even though not all feasible paths are needed to compute the invariant.

@@

\begin{figure}
  \begin{minipage}{.3\linewidth}
    \lstinputlisting[label=lst:gopan_reps]{gopan_reps.c}
  \end{minipage}
\hfill
\begin{minipage}{.5\linewidth}
\includegraphics[scale=0.75]{gopan_reps}
\vspace{-1ex}
\begin{equation}
y \leq x \;\land\; y \leq 102-x \;\land\; y \geq 0.\label{eqn:triangle}
\end{equation}
\end{minipage}
\caption{Example program and its invariant: the piecewise linear, solid line is the strongest invariant, the grayed polyhedron is its convex hull.}
\label{fig:gopan_reps_invariant} 
\end{figure}

>>>>

\usepackage{ifthen}
\newboolean{draft}
%\setboolean{draft}{true}
\setboolean{draft}{false}

\ifthenelse{\boolean{draft}}{
  \newcommand{\avirer}[1]{{\color{red} #1}}
  \newcommand{\MM}[1]{{\color{blue} TODO(MM): #1}}
  \newcommand{\JH}[1]{{\color{teal} TODO(JH): #1}}
  \newcommand{\DM}[1]{{\color{violet} TODO(DM): #1}}
}{
  \newcommand{\avirer}[1]{}
  \newcommand{\MM}[1]{}
  \newcommand{\JH}[1]{}
  \newcommand{\DM}[1]{}
}

@@

\avirer{
\begin{figure}
\MM{J'aime bien cette figure, qui montre en un coup d'oeil l'idée,
  mais elle prend vraiment beaucoup de place, je propose de
  supprimer.}

\centering
\begin{minipage}[c]{.21\textwidth}
\begin{tikzpicture}[->,>=stealth',auto,node distance=.2cm and .5cm,
                    semithick,font=\footnotesize]

@@

  \path [transition] 
		(n0) edge  [out=0, in=0]            node {} (n9);
  \path [transition] 
		(n0) edge  [out=180, in=180]        node {} (n9);
  \path [transition] 
		(n0) edge  [out=205, in=155]            node {} (n9);
  \path [transition] 
		(n0) edge  [out=230, in=130]            node {} (n9);
  \path [transition] 
		(n0) edge  [out=255, in=105]            node {} (n9);
  \path [transition] 
		(n0) edge  [out=-25, in=25]            node {} (n9);
  \path [transition] 
		(n0) edge  [out=-50, in=50]            node {} (n9);
  \path [transition] 
		(n0) edge  [out=-75, in=75]            node {} (n9);
\end{tikzpicture}
\end{minipage}
\caption{Expansion of the transition graph into a multigraph.}
\label{fig:multigraph}
\end{figure}
}

Classical interval analysis on this program yields $\lstinline|x_old| \in [-100000,100000]$.
We have transformed the first program into the second, manually pruning out infeasible paths; yet in general the resulting program could be exponentially larger than the first \avirer{(as in Fig.~\ref{fig:multigraph})}, even though not all feasible paths are needed to compute the invariant.

@@

\begin{figure}
  \begin{minipage}{.3\linewidth}
    \lstinputlisting[label=lst:gopan_reps]{gopan_reps.c}
  \end{minipage}
\hfill
\begin{minipage}{.5\linewidth}
\includegraphics[scale=0.7]{gopan_reps}
\vspace{-1em}
\begin{equation}
y \leq x \;\land\; y \leq 102-x \;\land\; y \geq 0.\label{eqn:triangle}
\end{equation}
\end{minipage}
\caption{Example program and its invariant: the piecewise linear, solid line is the strongest invariant, the grayed polyhedron is its convex hull.}
\label{fig:gopan_reps_invariant} 
\end{figure}
